The Unintended Consequences of Energy Reduction

### 2024-02-15 paper/paper.qmd
Added estimand to intro
Started ssrp files

---
title: "The Unintended Consequences of Energy Reduction"
subtitle: "How an Act of Environmental Protection Led to the Deaths of Many"
author:
  - Yi Fei Pang
  - Irene Hyunh
  - Tara Chakkithara
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "Nuclear energy is a clean power source that produces electricity while operating with low-carbon emissions. Although nuclear power generation has its advantages, many concerns have been raised regarding its safety after the Fukushima nuclear accident of 2011. This paper analyzes the utilization of nuclear energy, the price of electricity and electricity consumption, and the temperature-mortality relationship in Japan before and after the accident. We reveal that the use of nuclear energy in Japan sharply decreased following the nuclear accident, resulting in a power shortage scare and surge in electricity prices across Japan. This prompted the country’s government to push an energy saving mindset to the public, and as a result, electricity consumption plummeted. However, we find that the government’s efforts created adverse effects as days with high temperatures coupled with an energy saving mindset led to a higher mortality rate and a shift to fossil fuel dependent energy poses grave consequences to the environment. These findings prompt discussions about the true cost of energy saving."
pdf-engine: pdflatex
format:
  pdf:
    documentclass: article
    geometry:
      - top=30mm
      - left=20mm
      - heightrounded
include: false
warning: false
message: false
number-sections: true
bibliography: references.bib
---

@@

In this paper, we follow He and Tanaka’s paper (2019) to produce a reproduction of their findings and discuss further about Japan’s future as their government reverses their stance on nuclear energy and begins restarting the use of old power plants as a response to fossil fuel shortages and the public pressure to reduce the country’s carbon footprint. We analyze the major reduction in energy consumption from 2005 to 2015 caused by the decline in nuclear energy usage, the sharp increase in electricity prices, and the energy saving campaign pushed by the Japanese government in order to investigate their impact on the mortality rate related to high temperatures. We find that the mortality rate increases as energy consumption decreases. An important finding is that air conditioner usage plays a vital role in preventing deaths related to high temperatures. Therefore, the pressure to conserve energy and hence not utilize air conditioners, increases the mortality rate in Japan.

>>>>

---
title: "The Unintended Consequences of Energy Reduction"
subtitle: "How an Act of Environmental Protection Led to the Deaths of Many"
author:
  - Yi Fei Pang
  - Irene Hyunh
  - Tara Chakkithara
thanks: "Code and data are available at: https://github.com/apang00/Energy-Policy.git SSRP replication available at:"
date: today
date-format: long
abstract: "Nuclear energy is a clean power source that produces electricity while operating with low-carbon emissions. Although nuclear power generation has its advantages, many concerns have been raised regarding its safety after the Fukushima nuclear accident of 2011. This paper analyzes the utilization of nuclear energy, the price of electricity and electricity consumption, and the temperature-mortality relationship in Japan before and after the accident. We reveal that the use of nuclear energy in Japan sharply decreased following the nuclear accident, resulting in a power shortage scare and surge in electricity prices across Japan. This prompted the country’s government to push an energy saving mindset to the public, and as a result, electricity consumption plummeted. However, we find that the government’s efforts created adverse effects as days with high temperatures coupled with an energy saving mindset led to a higher mortality rate and a shift to fossil fuel dependent energy poses grave consequences to the environment. These findings prompt discussions about the true cost of energy saving."
pdf-engine: pdflatex
format:
  pdf:
    documentclass: article
    geometry:
      - top=30mm
      - left=20mm
      - heightrounded
include: false
warning: false
message: false
number-sections: true
bibliography: references.bib
---

@@

In this paper, we follow He and Tanaka’s paper (2019) to produce a reproduction of their findings and discuss further about Japan’s future as their government reverses their stance on nuclear energy and begins restarting the use of old power plants as a response to fossil fuel shortages and the public pressure to reduce the country’s carbon footprint. The estimand for our study is the effect of energy price on energy consumption. We analyze the major reduction in energy consumption from 2005 to 2015 caused by the decline in nuclear energy usage, the sharp increase in electricity prices, and the energy saving campaign pushed by the Japanese government in order to investigate their impact on the mortality rate related to high temperatures. We find that the mortality rate increases as energy consumption decreases. An important finding is that air conditioner usage plays a vital role in preventing deaths related to high temperatures. Therefore, the pressure to conserve energy and hence not utilize air conditioners, increases the mortality rate in Japan.
